---
title: "Kickstarter Analysis Proposal"
subtitle: "10/9/2020"
author: "The Laureates: Farzeen Najam, Olivia Olsher, Vincent Liu, Emile Therrien"
output: pdf_document
---

### Introduction
Have you ever had an ambitious idea but did not have resources to pursue it? Kickstarter is a crowdfunding platform for creators who need support for their projects. Since launching in 2009, 19 million people have pledged to back up projects, and nearly 190,000 projects have been successfully funded.
 
However, many more projects failed to reach their goals, and our group is interested in analyzing what made projects succeed and fail. The dataset that we use comes from Kaggle, which contains Kickstarter projects up until January 2018.
 
We will be exploring which variables influence the success of a Kickstarter project by observing which types of projects are more likely to be funded. Our questions include:

* Does the amount of money a project asks for influence it’s chance of success?
* Does the category of project influence it’s chance of success?

Our hypotheses include:

* The more money the project asks for, the less successful it will be in terms of getting funding.
* The category “Technology” will be the most likely funded type of projects.



### Data description
This data set contains 15 variables and 378,661 observations, where each observation is one kickstarter project.

The categorical variables include the name of each project, the category of each project (music, narrative film, restaurant, etc.), a broader category of each (food, film, publishing, etc.), the crowdsourcing currency, the state of each project (failed, successful, or cancelled), and the country of origin for each project.

The numerical data are the project’s ID number, the monetary goal for each, the money pledged to each project, how many backers of each project; there are three numerical variables that are not self-explanatory, usd_pledged: conversion in US dollars of the pledged column (conversion done by kickstarter), usd_pledge_real: conversion in US dollars of the pledged column (conversion from Fixer.io API), and usd_goal_real: conversion in US dollars of the goal column (conversion from Fixer.io API).

There are also two date columns, one for the project launch and the other for the crowdsourcing deadline.

The data were collected from Kickstarter Platform likely using web scraping methods on their own site, to be used by data scientists to model whether or not a project will be successful or not when it is launched.


### Glimpse of data

```{r file-glimpse, eval=TRUE, warning=FALSE, message=FALSE}
library(tidyverse)

kickstarter <- read_csv("data/ks-projects-201801.csv")
glimpse(kickstarter)

```

### Explorative Data Analysis

Overview of project state:

```{r state-analysis}
kickstarter %>%
  group_by(state) %>%
  count()

kickstarter %>%
  filter(state == "successful") %>%
  summarize(success_rate = n()/nrow(kickstarter))
```

Overview of usd dollars pledged and goal:

```{r pledged-and-goal-overview}
overview_usd_pledged_real <- kickstarter %>%
  summarize(mean_usd_pledged_real = mean(usd_pledged_real),
            median_usd_pledged_real = median(usd_pledged_real),
            sd_usd_pledged_real = sd(usd_pledged_real))

overview_usd_goal_real <- kickstarter %>%
  summarize(mean_usd_goal_real = mean(usd_goal_real),
            median_usd_goal_real = median(usd_goal_real),
            sd_usd_goal_real = sd(usd_goal_real))

overview_usd_pledged_real
overview_usd_goal_real
```

### Project Goal & Success

*Question*: Is the project goal (amount of money a project asks for) associated with whether it is successful?

*Hypotheses*:

* $H_0$: There is no relationship between a project's goal and whether a project is successful or not.
* $H_1$: There is a relationship between a project's goal and whether a project is successful or not.

Create a new data frame with projects that are no longer live:

```{r exclude-ongoing-projects}
# Exclude ongoing projects
kickstarter_not_live <- kickstarter %>%
  filter(state != "live")
```

Create a new variable named usd_goal_real_tier to classify usd_goal_real into tiers:

```{r mutate-goal-tiers}
# perhaps need a better way to categorize values in this column
kickstarter_not_live <- kickstarter_not_live %>%
  mutate(usd_goal_real_tier = case_when(
    usd_goal_real < 1000 ~ 1,
    usd_goal_real >= 1000 & usd_goal_real < 5000 ~ 2,
    usd_goal_real >= 5000 & usd_goal_real < 10000 ~ 3,
    usd_goal_real >= 10000 & usd_goal_real < 20000 ~ 4,
    usd_goal_real >= 20000 & usd_goal_real < 100000 ~ 5,
    usd_goal_real >= 100000 & usd_goal_real < 500000 ~ 6,
    usd_goal_real >= 500000 ~ 7,
  ))

kickstarter_not_live %>%
  group_by(usd_goal_real_tier) %>%
  count()
```

Create a new variable for success state

```{r mutate-success-state}
kickstarter_not_live <- kickstarter_not_live %>%
  mutate(success_state = if_else(state == "successful", 1, 0))
```

We'll run a chi-square test at alpha = 0.05.

```{r goal-state-association}
chisq.test(table(kickstarter_not_live$success_state, kickstarter_not_live$usd_goal_real_tier))
```

Our test statistic was 19624, which has a chi-square distribution with 6 degree of freedom under $H_0$. This corresponds to a p-value less than 2.2e-16. So our decision is to reject $H_0$, and there is sufficient evidence that there is a relationship between a project's goal and a project's state.

### Project Goal Amount & Success

*Claim*: The more money the project asks for, the less successful it will be in terms of getting funding.

### Emile and Olivia

* Does the category of project influence it’s chance of success?
* The category “Technology” will be the most likely funded type of projects.

limitations: possible crossover in the main_categories that we cannot screen
for

```{r category-success}
kickstart_success = kickstarter %>% 
  mutate(
    project_funding_ratio = pledged/goal,
    success = case_when(
      project_funding_ratio >= 1 ~ "achieved",
      project_funding_ratio < 1 ~ "not achieved"
    )
  )

kickstater_success_ratios = kickstart_success %>% 
  group_by(success, main_category) %>% 
  count(success) %>% 
  mutate(
    sum = 137042+241619
  ) %>% 
  filter(success == "achieved") %>% 
  mutate(
    proportion_achieved = n/sum
  )

kickstater_success_ratios
  
  

ggplot(data = kickstart_success, mapping  =  
         aes(x = success, fill = main_category)) +
  facet_wrap(main_category ~ .) +
  geom_histogram(stat = "count") +
  theme(legend.position = "none")

ggplot(data = kickstater_success_ratios, aes(x = success, y = proportion_achieved, fill = main_category)) +
  facet_wrap(main_category ~ .) +
  geom_bar() +
  theme(legend.position = "none")

```




